The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2024-03-26 exp-resurgence.tex
Revise first look at thimble integrals

\textcolor{RoyalBlue}{
Borel regularity is a new approach to Borel summability, that present Borel summation as a regularization process and it explains the effectiveness of Borel summability, namely that Borel summation can be used to reconstruct analytic functions from their asymptotics. \textcolor{orange}{[Highlight analytic perspective more?]} Borel regular functions shows up in two classes of examples: as solutions of certain level $1$ ODEs and as integrals over Lefschetz thimbles. In addition, we give a geometric description of the Borel plane.}
\end{abstract}
\tableofcontents
%
%
%
\section{Introduction}
\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
%%\subsection{A familiar process: Borel summation}\label{intro:summation}
You can often find a formal power series %\textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
\begin{equation}
\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel-rescaled-1}
\end{equation}
behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above. Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution 
\begin{equation}
e^{z} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{72} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{31104} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{6718464} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
\end{equation}
and its constant multiples (see \cite[equation 10.40.1]{dlmf}). As another example, you might rewrite the integral

\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(4 u^3 - 3 u\right)\right]\,du \]
as
\[ e^{z}\, \frac{1}{2\sqrt{3}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{\sqrt{3}}{9} t + \frac{5}{72} t^2 - \frac{4\sqrt{3}}{243} t^3 + \frac{385}{31104} t^4 - \frac{7\sqrt{3}}{2187} t^5 + \frac{17017}{6718464} t^6 - \ldots \right] dt \]
using the substitution $\tfrac{1}{2} t^2 = 4 u^3 - 3 u + 1$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel-ex}---up to a constant.\begin{verify}
    see Mathematica document.
\end{verify}

@@

The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
\begin{enumerate}
\item Solving a level~$1$ linear ODE \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}. Equation~\eqref{eqn:bessel-rescaled-1} is an example. More generally, we will consider equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form
\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}), \]
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every root of $P$, and $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. We will restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}).

The form of $\mathcal{P}$ derives from Equation~2.2.3 of \cite[pag. 105]{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$. Borel summation is more involved for the nonlinear ones, raising the question of whether our analysis generalizes.
%
\item Evaluating a certain kind of integral: a one-dimensional {\em thimble integral}
%
\begin{equation*}
I(z)\defeq\int_{\Lambda}\exp\big[-z f\big] \nu
\end{equation*}
where $f\colon X\to \mathbb{C}$ is a holomorphic functions with isolated and non-degenerate critical points, $X$ is $1$-dimensional complex manifold, $\nu\in\Omega^1(X)$ is holomorphic $1$-form in $X$ and $\Lambda$ is a suitable contour such that $I(z)$ is a holomorphic function of $z$.  
\end{enumerate}
These two problems are closely linked. By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies. Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.

@@

We will present the statements of our main results in Section~\ref{sec:why_borel_ODE} and Section~\ref{sec:why_borel_thibmle}, for ODEs and thimble integrals, respectively. The corresponding proofs are collected in Section~\ref{sec:proof_main_results}.
\subsubsection{Why does Borel summation work for solutions of level $1$ ODEs?}\label{sec:why_borel_ODE}
%\textcolor{DarkCyan}{[Let us try to move some technical detail from here to the section where the result is proved. For example:]}
%
Consider a linear level-$1$ differential operator $\mathcal{P}$ of the form described in~Section~\ref{borel-reg:explanatory-power}. This operator will always have an irregular singularity at $z = \infty$.
\begin{verify}
\par
Turn the ODE into a system: assume 
\begin{align*}
P(\lambda) & = P_0 + P_1 \lambda + \ldots + P_d \lambda^d \\
Q(\lambda) & = Q_0 + Q_1 \lambda + \ldots + Q_{d-1} \lambda^{d-1}
\end{align*}
then the ODE $\mathcal{P}\psi=0$ is equivalent to the system 
    \begin{equation}
        \frac{d}{dz}Y= B(z) Y 
    \end{equation}
    \[
    B(z)=\begin{pmatrix}
            0 & 1 & 0 & \ldots & 0 \\
            0 & 0 & 1 & \ldots & 0 \\
            \vdots & &\ddots & & 1\\
            b_{1}(z) & & b_j(z) & \ldots & b_{d-1}(z)
        \end{pmatrix}, \quad Y=\begin{pmatrix}
            \psi \\
            \psi ' \\
            \vdots \\
            \psi^{(d-1)}
        \end{pmatrix}
    \]

@@

\subsubsection{Why does Borel summation work for thimble integrals?}\label{sec:why_borel_thibmle}

@@

To make sense of this formula, we ask for the following conditions.
\item The base point $b$ is in the domain of $\zeta$. Once we have this, we can continue $\zeta$ along the whole ray $\Gamma_b^\theta$.
\item The ray $\Gamma_b^\theta$ avoids the branch points after leaving $b$.
\item The integral converges. We guarantee this by asking for a pair of simpler conditions.
%\color{RoyalBlue}
\item With respect to the flat metric, $f$ is uniformly of exponential type $\Lambda$ along $\Gamma_b^\theta$, and is locally integrable throughout.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $. We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} \textcolor{Pink}{[Revise]} Following \cite{reg-sing-volterra}, we require $f \in \singexp{\sigma}{\Lambda}(\Omega_b)$, with $\sigma>-1$.\footnote{The condition $\sigma>-1$ guarantees the integrability at $\zeta=b$.} The set $\Omega_b$ is a tubular neighbourhood of $\Gamma_b^\theta$. 
\item The value of $z$ is in the half-plane $H^{\theta}_\Lambda$ cut out by the inequality $\Re(e^{i\theta} z) > \Lambda$.
\subsubsection{The Laplace transform over a branch point}
When $b$ is a branch point, we can still use formula~\eqref{laplace:int} to define $\laplace_\zeta^\theta f$ on $T_b^*B$, as long as we take care of a few subtleties. Thanks to the labeling choices we made at the end of Section~\ref{transl:dir}, the extended angle $\theta \in \R$ still picks out a ray $\Gamma_b^\theta$. The function $z$ is defined on $T_b^*B^{\otimes n}$, where $2\pi n$ is cone angle at $b$, so we pull it back to $T^*_bB$ along the $n$th-power map. This amounts to substituting $w_b^n$ for $z$ in formula~\eqref{laplace:int}. The half-plane $z \in H_{\theta}$ in $T_b^*B^{\otimes n}$ pulls back to $n$ sectors of angle $\pi/n$ in $T_b^*B$. We only define $\laplace_\zeta^\theta f$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
%\subsection{The geometry of the Borel transform}
  %\item The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$. It's a formal inverse of the $\laplace_{\zeta, 0}$.
  %\item Formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$, we can extend the Borel transform to trans-series, defining $\borel\textcolor{orange}{_\zeta} \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta \rrbracket$ as the formal inverse of $\laplace_{\zeta, \alpha}$.
   % \item In other words, when $\borel_\zeta$ acts on formal power series, it formally inverts $\laplace_\zeta$ on the cotangent fiber over $0$. \textcolor{magenta}{When it acts on other trans-monomials, it formally inverts $\laplace_\zeta$ on other cotangent fibers. [Not quite\ldots figure out how to make this precise.] }
  %\item consequently, $\borel_{\zeta_\alpha}$ acts on trans-monomials $e^{z\alpha}\C\llbracket z^{-1}\rrbracket$ and it formally inverts $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $0$. 
\subsubsection{Change of translation chart}\label{sec:change-translation}
Let $b \in B$ be an ordinary point, and let $\zeta_b$ be the coordinate on $B$ for which $\zeta = \zeta(b) + \zeta_b$. Then the Laplace transform $\laplace_{\zeta_b,0}$, which turns functions on $B$ into functions on $T^*_{b}B$, is compatible with $\laplace_{\zeta,b}$.  
\begin{lemma}\label{translation}

@@

@@

%%It follows that $\borel_\zeta$ is a formal inverse of the $\laplace_{\zeta, 0}$: let $\varphi=\sum_{n=0}^{\infty}a_n \zeta^n$
%\begin{align*}
 %   \borel_\zeta \laplace_{\zeta}\varphi&=\borel_\zeta \left[\int_{\Gamma_{\zeta,0}}e^{-z\zeta} \varphi d\zeta\right]\\
  %  &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n \int_{\Gamma_{\zeta,0}} e^{-z\zeta}\zeta^n d\zeta\right]\\
  %  &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n z^{-n-1}n! \right]\\
  %  &=\sum_{n=0}^{\infty}a_n \frac{\zeta^n}{n!}
%\end{align*}
%where in the second step we formally interchange the integral and the sum. 
%\color{black}
\subsubsection{Action on transseries}\label{sec:action_transseries}

A transseries is a generalization of usual power series, whose building blocks (called trans-monomials) are of the form $e^{\alpha_n z}\varphi_n$ where $\alpha_n$ is a sequence of complex numbers such that \textcolor{PaleVioletRed}{[what does this mean?]} $0=\alpha_0 e^{-i\theta}< \alpha_1 e^{-i\theta}<...<\alpha_n e^{-i\theta}<...$ and $\varphi_n\in\C\llbracket z^{-1}\rrbracket$ for every $n$:

@@

It's natural to ask whether we can extend the definition of $\borel_\zeta$ to transseries, and we will achieve it using the relationship between $\laplace_{\zeta, \alpha}$ and $\laplace_{\zeta_\alpha, 0}$ in identity~\eqref{change-chart}. 
\begin{definition}
    The action of $\borel_\zeta$ on trans-monomials is the formal inverse of $\laplace_{\zeta,\alpha}$
    \[\laplace_{\zeta,\alpha}\borel_\zeta\big[e^{-z\alpha}z^{-n-1}\big]=e^{-z\alpha}z^{-n-1}\]
    %\begin{center}
%\begin{tikzcd}[every arrow/.append style={shift left}]
 %e^{-z\alpha}\{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta}} \\ \{1, \zeta_\alpha, \zeta_\alpha^2, \zeta_\alpha^3, \ldots\} \arrow{u}{\laplace_{\zeta,\alpha}}
%\end{tikzcd}
%\end{center}
    and it extends by linearity to transseries. 
\end{definition}
In particular, from identity~\eqref{change-chart} we deduce 
\begin{align*}
    e^{-z\alpha}z^{-n-1}&=e^{-z\alpha}\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\zeta\alpha}z^{-n-1}\big]\\
     z^{-n-1}&=\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\zeta\alpha}z^{-n-1}\big]
\end{align*}
and taking the inverse of $\laplace_{\zeta_\alpha,0}$ we find
%Indeed it is possible by formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$ (see Section \ref{translation} identity \eqref{change-chart}).

@@

Let us run through the proof of Theorem~3, specialized to the case we consider in Theorem~4. First, picking an arbitrary point $b \in \Omega_\alpha$, we show that the {\em prototype solution}
\[ \solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \]
lies in the space $\singexpalg{\tau_\alpha - 1}(\Upsilon)$ and satisfies the equation $\solproto = \hardpart^\alpha \solproto$. We then look for a perturbation $\solptb$ that makes $\solwhole = \solproto + \solptb$ a solution of the Volterra equation we are trying to solve. This is equivalent to solving the inhomogeneous equation
\begin{equation}\label{eqn:inhomog-volterra}
\solptb = \softpart^\alpha \solproto + \volterra^\alpha \solptb
\end{equation}
The central idea of the proof is to show that $\softpart^\alpha$ maps $\solproto$, and in fact all of $\singexpalg{\tau_\alpha - 1}(\Upsilon)$, into $\singexpalg{\tau_\alpha}(\Upsilon)$ \textcolor{orange}{[check]}, and that $\volterra^\alpha$ is a contraction of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ when $\Lambda$ is large enough. It follows, by the contraction mapping theorem, that equation~\eqref{eqn:inhomog-volterra} has a unique solution $\solptb$ in $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$. More explicitly, we can solve equation~\eqref{eqn:inhomog-volterra} by Picard iteration. Defining
\begin{align*}
\solptb^{(0)} & = \softpart^\alpha \solproto \\
\solptb^{(1)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(0)} \\
\solptb^{(2)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(1)} \\
\solptb^{(3)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(2)} \\
& \;\;\vdots
\end{align*}
we get a sequence of functions that converges in $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ to a solution.

>>>>

\textcolor{RoyalBlue}{
Borel regularity is a new approach to Borel summability, that present Borel summation as a regularization process and it explains the effectiveness of Borel summability, namely that Borel summation can be used to reconstruct analytic functions from their asymptotics. \textcolor{orange}{[Highlight analytic perspective more?]} Borel regular functions shows up in two classes of examples: as solutions of certain level $1$ ODEs and as integrals over Lefschetz thimbles. In addition, we give a geometric description of the Borel plane.}
\end{abstract}
\tableofcontents
%
%
%
\section{Introduction}
\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
%%\subsection{A familiar process: Borel summation}\label{intro:summation}
You can often find a formal power series %\textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
\begin{equation}
\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel_rescaled_ex}
\end{equation}
behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above. Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution 
\begin{equation}
e^{z} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{72} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{31104} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{6718464} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel_ex}
\end{equation}
and its constant multiples (see \cite[equation 10.40.1]{dlmf}). As another example, you might rewrite the integral
\begin{equation}\label{int:bessel_ex}
\Phi = \int_{\Lambda} \exp\left[-z \left(4 u^3 - 3 u\right)\right]\,du
\end{equation}
as
\[ e^{z}\, \frac{1}{2\sqrt{3}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{\sqrt{3}}{9} t + \frac{5}{72} t^2 - \frac{4\sqrt{3}}{243} t^3 + \frac{385}{31104} t^4 - \frac{7\sqrt{3}}{2187} t^5 + \frac{17017}{6718464} t^6 - \ldots \right] dt \]
using the substitution $\tfrac{1}{2} t^2 = 4 u^3 - 3 u + 1$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel_ex}, up to a constant. \begin{verify}[See Mathematica document.]\end{verify}

@@

The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
\begin{enumerate}
\item Solving a level~$1$ linear ODE \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}. Equation~\eqref{eqn:bessel_rescaled_ex} is an example. More generally, we will consider equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form
\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}), \]
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every root of $P$, and $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. We will restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}).

The form of $\mathcal{P}$ derives from Equation~2.2.3 of \cite[pag. 105]{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$. Borel summation is more involved for the nonlinear ones, raising the question of whether our analysis generalizes.
%
\item Evaluating a one-dimensional {\em thimble integral}. Integral~\eqref{int:bessel_ex} is an example. More generally, we will consider integrals of the form
\begin{equation*}
I = \int_{\Lambda}e^{-zf}\,\nu,
\end{equation*}
where $X$ is $1$-dimensional complex manifold; $f \maps X \to \C$ is a holomorphic function with isolated, non-degenerate critical points; $\nu \in \Omega^1(X)$ is holomorphic $1$-form on $X$, and $\Lambda$ is {\em Lefschetz thimble}---a type of contour described in Section~\ref{sec:why_borel_thimble}. Under these conditions, $I$ is a holomorphic function of $z$.
\end{enumerate}
These two problems are closely linked. By playing with derivatives of a thimble integral, you can often find a linear ODE that the integral satisfies. Conversely, for many classical ODEs, there are useful bases of thimble integral solutions.

@@

We will present the statements of our main results in Section~\ref{sec:why_borel_ODE} and Section~\ref{sec:why_borel_thimble}, for ODEs and thimble integrals, respectively. The corresponding proofs are collected in Section~\ref{sec:proof_main_results}.
\subsubsection{Why does Borel summation work for solutions of level $1$ ODEs?}\label{sec:why_borel_ODE}
%\textcolor{DarkCyan}{[Let us try to move some technical detail from here to the section where the result is proved. For example:]}
%
Consider a linear level-$1$ differential operator $\mathcal{P}$ of the form described in~Section~\ref{borel-reg:explanatory-power}. This operator will always have an irregular singularity at $z = \infty$.
\begin{verify}
\par
Turn the ODE into a system: assume 
\begin{align*}
P(\lambda) & = P_0 + P_1 \lambda + \ldots + P_d \lambda^d \\
Q(\lambda) & = Q_0 + Q_1 \lambda + \ldots + Q_{d-1} \lambda^{d-1}
\end{align*}
then the ODE $\mathcal{P}\psi=0$ is equivalent to the system 
    \begin{equation}
        \frac{d}{dz}Y= B(z) Y 
    \end{equation}
    \[
    B(z)=\begin{pmatrix}
            0 & 1 & 0 & \ldots & 0 \\
            0 & 0 & 1 & \ldots & 0 \\
            \vdots & &\ddots & & 1\\
            b_{1}(z) & & b_j(z) & \ldots & b_{d-1}(z)
        \end{pmatrix}, \quad Y=\begin{pmatrix}
            \psi \\
            \psi ' \\
            \vdots \\
            \psi^{(d-1)}
        \end{pmatrix}
    \]

@@

\subsubsection{Why does Borel summation work for thimble integrals?}\label{sec:why_borel_thimble}

@@

To make sense of this formula, we ask for the following conditions.
\begin{itemize}
\item The base point $b$ is in the domain of $\zeta$. Once we have this, we can continue $\zeta$ along the whole ray $\Gamma_b^\theta$.
\item The ray $\Gamma_b^\theta$ avoids the branch points after leaving $b$.
\item The integral converges. We guarantee this by asking for a pair of simpler conditions.
%\color{RoyalBlue}
\begin{itemize}
\item With respect to the flat metric, $f$ is uniformly of exponential type $\Lambda$ along $\Gamma_b^\theta$, and is locally integrable throughout.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $. We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} \textcolor{Pink}{[Revise]} Following \cite{reg-sing-volterra}, we require $f \in \singexp{\sigma}{\Lambda}(\Omega_b)$, with $\sigma>-1$.\footnote{The condition $\sigma>-1$ guarantees the integrability at $\zeta=b$.} The set $\Omega_b$ is a tubular neighbourhood of $\Gamma_b^\theta$. 
\item The value of $z$ is in the half-plane $H^{\theta}_\Lambda$ cut out by the inequality $\Re(e^{i\theta} z) > \Lambda$.
\end{itemize}
\end{itemize}
\color{black}
\subsubsection{The Laplace transform over a branch point}
When $b$ is a branch point, we can still use formula~\eqref{laplace:int} to define $\laplace_\zeta^\theta f$ on $T_b^*B$, as long as we take care of a few subtleties. Thanks to the labeling choices we made at the end of Section~\ref{transl:dir}, the extended angle $\theta \in \R$ still picks out a ray $\Gamma_b^\theta$. The function $z$ is defined on $T_b^*B^{\otimes n}$, where $2\pi n$ is cone angle at $b$, so we pull it back to $T^*_bB$ along the $n$th-power map. This amounts to substituting $w_b^n$ for $z$ in formula~\eqref{laplace:int}. The half-plane $z \in H_{\theta}$ in $T_b^*B^{\otimes n}$ pulls back to $n$ sectors of angle $\pi/n$ in $T_b^*B$. We only define $\laplace_\zeta^\theta f$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
%\color{gray}
%\subsection{The geometry of the Borel transform}
%\begin{itemize}
  %\item The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$. It's a formal inverse of the $\laplace_{\zeta, 0}$.
  %\item Formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$, we can extend the Borel transform to trans-series, defining $\borel\textcolor{orange}{_\zeta} \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta \rrbracket$ as the formal inverse of $\laplace_{\zeta, \alpha}$.
  %\begin{itemize}
   % \item In other words, when $\borel_\zeta$ acts on formal power series, it formally inverts $\laplace_\zeta$ on the cotangent fiber over $0$. \textcolor{magenta}{When it acts on other trans-monomials, it formally inverts $\laplace_\zeta$ on other cotangent fibers. [Not quite\ldots figure out how to make this precise.] }
  %\end{itemize}
  %\item consequently, $\borel_{\zeta_\alpha}$ acts on trans-monomials $e^{z\alpha}\C\llbracket z^{-1}\rrbracket$ and it formally inverts $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $0$. 
%\end{itemize}
%\color{black}
\subsubsection{Change of translation chart}\label{sec:change-translation}
Suppose $\zeta$ is a translation chart on $B$, and $\zeta = \alpha$ is an ordinary point. Let $\zeta_\alpha$ be the translation chart with $\zeta = \alpha + \zeta_\alpha$. The Laplace transforms $\laplace_{\zeta_\alpha, 0}$ and $\laplace_{\zeta, \alpha}$, which both turn functions on $B$ into functions on $T^*_{\zeta = \alpha}B$, are related in the following way.

\textcolor{RoyalBlue}{Let $b \in B$ be an ordinary point, and let $\zeta_b$ be the coordinate on $B$ for which $\zeta = \zeta(b) + \zeta_b$. Then the Laplace transform $\laplace_{\zeta_b,0}$, which turns functions on $B$ into functions on $T^*_{b}B$, is compatible with $\laplace_{\zeta,b}$.}
\begin{lemma}%%\label{translation}

@@

\begin{lemma}%%\label{translation}

@@

%%It follows that $\borel_\zeta$ is a formal inverse of the $\laplace_{\zeta, 0}$: let $\varphi=\sum_{n=0}^{\infty}a_n \zeta^n$
%\begin{align*}
 %   \borel_\zeta \laplace_{\zeta}\varphi&=\borel_\zeta \left[\int_{\Gamma_{\zeta,0}}e^{-z\zeta} \varphi d\zeta\right]\\
  %  &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n \int_{\Gamma_{\zeta,0}} e^{-z\zeta}\zeta^n d\zeta\right]\\
  %  &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n z^{-n-1}n! \right]\\
  %  &=\sum_{n=0}^{\infty}a_n \frac{\zeta^n}{n!}
%\end{align*}
%where in the second step we formally interchange the integral and the sum. 
%\color{black}
\subsubsection{Action on transseries}\label{sec:action_transseries}
%
\color{DarkTurquoise}
\color{RoyalBlue}
A transseries is a generalization of usual power series, whose building blocks (called trans-monomials) are of the form $e^{\alpha_n z}\varphi_n$ where $\alpha_n$ is a sequence of complex numbers such that \textcolor{PaleVioletRed}{[what does this mean?]} $0=\alpha_0 e^{-i\theta}< \alpha_1 e^{-i\theta}<...<\alpha_n e^{-i\theta}<...$ and $\varphi_n\in\C\llbracket z^{-1}\rrbracket$ for every $n$:

@@

It's natural to ask whether we can extend the definition of $\borel_\zeta$ to transseries, and we will achieve it using the relationship between $\laplace_{\zeta, \alpha}$ and $\laplace_{\zeta_\alpha, 0}$ in identity~\eqref{change-chart}.
\color{black}
\begin{definition}
    The action of $\borel_\zeta$ on trans-monomials is the formal inverse of $\laplace_{\zeta,\alpha}$
    \[\laplace_{\zeta,\alpha}\borel_\zeta\big[e^{-z\alpha}z^{-n-1}\big]=e^{-z\alpha}z^{-n-1}\]
    %\begin{center}
%\begin{tikzcd}[every arrow/.append style={shift left}]
 %e^{-z\alpha}\{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta}} \\ \{1, \zeta_\alpha, \zeta_\alpha^2, \zeta_\alpha^3, \ldots\} \arrow{u}{\laplace_{\zeta,\alpha}}
%\end{tikzcd}
%\end{center}
    and it extends by linearity to transseries. 
\end{definition}
In particular, from identity~\eqref{change-chart} we deduce 
\begin{align*}
    e^{-z\alpha}z^{-n-1}&=e^{-z\alpha}\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\zeta\alpha}z^{-n-1}\big]\\
     z^{-n-1}&=\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\zeta\alpha}z^{-n-1}\big]
\end{align*}
and taking the inverse of $\laplace_{\zeta_\alpha,0}$ we find
%Indeed it is possible by formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$ (see Section \ref{translation} identity \eqref{change-chart}).

@@

Let us run through the proof of Theorem~3, specialized to the case we consider in Theorem~4. First, picking an arbitrary point $b \in \Omega_\alpha$, we show that the {\em prototype solution}
\[ \solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \]
lies in the space $\singexpalg{\tau_\alpha - 1}(\Upsilon)$ and satisfies the equation $\solproto = \hardpart^\alpha \solproto$. We then look for a perturbation $\solptb$ that makes $\solwhole = \solproto + \solptb$ a solution of the Volterra equation we are trying to solve. This is equivalent to solving the inhomogeneous equation
\begin{equation}\label{eqn:inhomog-volterra}
\solptb = \softpart^\alpha \solproto + \volterra^\alpha \solptb
\end{equation}
The central idea of the proof is to show that $\softpart^\alpha$ maps $\solproto$, and in fact all of $\singexpalg{\tau_\alpha - 1}(\Upsilon)$, into $\singexpalg{\tau_\alpha}(\Upsilon)$ \textcolor{orange}{[check]}, and that $\volterra^\alpha$ is a contraction of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ when $\Lambda$ is large enough. It follows, by the contraction mapping theorem, that equation~\eqref{eqn:inhomog-volterra} has a unique solution $\solptb$ in $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$. More explicitly, we can solve equation~\eqref{eqn:inhomog-volterra} by fixed-point iteration. Defining
\begin{align*}
\solptb^{(0)} & = \softpart^\alpha \solproto \\
\solptb^{(1)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(0)} \\
\solptb^{(2)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(1)} \\
\solptb^{(3)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(2)} \\
& \;\;\vdots
\end{align*}
we get a sequence of functions that converges in $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ to a solution.
